---
title: "Online Harvest Survey Annual Summary Report"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc: true
    number_sections: true
params:
  inpath:
    value: x
  partypath:
    value: x
  year:
    value: x
---

```{r, libs, message = FALSE, warning = FALSE, echo = FALSE}

library(tidyverse)
library(ggnewscale)
library(MetBrewer)
library(DT)

# Input path
inpath <- params$inpath

# Read data 
invisible(read_dhs(inpath, year = as.character(params$year)))

# Add seaducks to the season metadata
all_seasons <- paste0("all_seasons_", as.character(params$year))
invisible(assign(all_seasons, add_seaducks(get(all_seasons)), envir = .GlobalEnv))

# Write tibble names to list for function compatibility
tibblelist <-
  vector("list", 3) %>% 
  set_names(
    all_seasons,
    paste0("daily_records_", as.character(params$year)),
    paste0("season_totals_", as.character(params$year)))
```

# Introduction

This is the `r params$year` season report for Harvest Survey online data.

## Check for missing data

For the season data (including daily records), what species are missing per state?

```{r, nodata2, message = FALSE, warning = FALSE, echo = F}
datatable(
  nodata(
    data = get(names(tibblelist[3])), 
    ref_data = get(names(tibblelist[1])), 
    species = "all",
    report = TRUE), 
  options = list(pageLength = 5))
```

## Hunters who submitted

### Season 

How many hunters submitted in the season data? Daily records excluded and data are only shown if days_hunted > 0.

#### Total

```{r, submitted1, message = FALSE, warning = FALSE, echo = F}
knitr::kable(
  submitted(get(names(tibblelist[3]))) %>% 
    rename(`Has submitted?` = has_submitted) %>% 
    mutate(prop = round(n/sum(n), 2)))
```

#### By species

```{r, submitted2, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 5, dpi = 300, out.width = 500, fig.align = "center", echo = F}

submitted(get(names(tibblelist[3])), type = "species", output = "plot") +
  scale_fill_manual(values = met.brewer("Hokusai3", 2)) + 
  theme(legend.position = "bottom")
```

### Daily

How many hunters submitted in the daily data? Records must have answered "yes" to has hunted.

#### Total

```{r, submitted4, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center", echo = F}
knitr::kable(
  submitted(get(names(tibblelist[2]))) %>% 
    rename(`Has submitted?` = has_submitted) %>% 
    mutate(prop = round(n/sum(n), 2)))
```

#### By species

```{r, submitted5, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center", echo = F}
submitted(get(names(tibblelist[2])), type = "species", output = "plot") +
  scale_fill_manual(values = met.brewer("Hokusai3", 2)) + 
  theme(legend.position = "bottom")
```

## Has hunted?

### Season

How many hunters hunted in the season data? Daily records have been excluded.

#### Total

```{r, hunted1, message = FALSE, warning = FALSE, echo = FALSE}

knitr::kable(
  hunted(get(names(tibblelist[3]))) %>% 
    mutate(
    days_hunted = 
      ifelse(
        str_detect(days_hunted, "NULL"), 
        NA, 
        days_hunted),
    has_hunted = ifelse(days_hunted > 0, "Y", "N")) %>% 
    group_by(has_hunted) %>% 
    summarize(sum_n = sum(n)) %>% 
    ungroup() %>% 
    rename(
      `Has hunted?` = has_hunted,
      n = sum_n) %>% 
    mutate(prop = round(n/sum(n), 2)))
```

#### By species

```{r, hunted2, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 5, dpi = 300, out.width = 500, fig.align = "center", echo  = F}

hunted(get(names(tibblelist[3])), type = "species", output = "plot") +
  scale_fill_manual(values = met.brewer("Hokusai3", 2)) + 
  theme(legend.position = "bottom")
```

# Party hunts and erroneous take

## Identify party hunts

Here are the manual corrections done to party hunt retrieved values with the `partyproof` function:

```{r, partyresults, message = FALSE, warning = FALSE, echo = F}
proofed_parties <-
  read.csv(paste0(params$partypath, "proofed_parties_", params$year, ".csv"))

datatable(
  proofed_parties %>% 
    select(-new_retrieved) %>% 
    rename(new_retrieved = retrieved), 
  options = list(pageLength = 5))
```

## Check for overdays

Are there any hunts submitted with an impossible number of days hunted?

### Season

```{r, overdays1, warning = FALSE, echo = F}
datatable(
  overdays(get(names(tibblelist[3])), get(names(tibblelist[1])))
)
```

### Daily 

```{r, overdays2, warning = FALSE, echo = F}
datatable(
  overdays(get(names(tibblelist[2])), get(names(tibblelist[1]))) 
)
```

## Check for overbags

### Season

What values are over the limit per species and state in the season totals data? Total retrieved values are divided by number of days hunted. Values over the daily limit per state and species are shown below.

```{r, overbags1, message = FALSE, warning = FALSE, echo = F}
datatable(
  overbags(get(names(tibblelist[3])), get(names(tibblelist[1]))) 
)
```

### Daily

What values in the retrieved field of daily data were over the limit per species and state?

```{r, overbags2, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center", echo  = F}
overbags(get(names(tibblelist[2])), get(names(tibblelist[1]))) %>% 
  rename(
    state = sampled_state,
    sp = sp_group_estimated) %>% 
  mutate(
    sp = ifelse(str_detect(sp, "Sea"), "Sea Ducks", sp)) %>% 
  left_join(
    tibble(
      state = state.name,
      state_abbr = state.abb),
    by = "state") %>% 
  mutate(bag_lim_label = "Bag limit") %>% 
  ggplot() + 
  geom_point(aes(x = state_abbr, y = bag_limit, shape = bag_lim_label), 
             color = "red", size = 6) + 
  geom_boxplot(aes(x = state_abbr, y = retrieved), show.legend = F) +
  theme_classic() + 
  labs(y = "Number of birds retrieved", x = "State", shape = "") +
  scale_shape_manual(values = "-", labels = "Bag limit") +
  theme(legend.position = "bottom") +
  facet_grid(
    ~sp, 
    scales = "free", 
    space = "free", 
    labeller = label_wrap_gen(width = 5))
```

```{r, overbags3, message = FALSE, warning = FALSE, echo = F}
datatable(
  overbags(get(names(tibblelist[2])), get(names(tibblelist[1])), summary = T) %>% 
    rename(
      state = sampled_state,
      sp = sp_group_estimated) %>% 
    mutate(
      sp = ifelse(str_detect(sp, "Sea"), "Sea Ducks", sp))
)
```

## Overbags lookup table

```{r, overbags4, message = FALSE, warning = FALSE, echo = F}

datatable(
  overbags(get(names(tibblelist[2])), get(names(tibblelist[1])), summary = F) %>% 
    rename(
      state = sampled_state,
      sp = sp_group_estimated) %>% 
    mutate(
      sp = 
        case_when(
          str_detect(sp, "Sea") ~ "SeaDucks", 
          str_detect(sp, "Mourning") ~ "MODO",
          str_detect(sp, "White") ~ "WWDO",
          str_detect(sp, "Crane") ~ "Cranes",
          TRUE ~ sp) %>% 
        str_remove_all(., " ")) %>% 
    pivot_wider(
      id_cols = 
        c("selected_hunterID", "surveyID", "state", "county", "harvested_date"),
      values_from = retrieved,
      names_from = sp) %>% 
    mutate(over = "Y") %>% 
    bind_rows(
      overbags(get(names(tibblelist[2])), get(names(tibblelist[1])), over = F) %>% 
        rename(
          sp = sp_group_estimated,
          state = sampled_state) %>% 
        mutate(
          sp = 
            case_when(
              str_detect(sp, "Sea") ~ "SeaDucks", 
              str_detect(sp, "Mourning") ~ "MODO",
              str_detect(sp, "White") ~ "WWDO",
              str_detect(sp, "Crane") ~ "Cranes",
              TRUE ~ sp) %>% 
            str_remove_all(., " ")) %>% 
        pivot_wider(
          id_cols = 
            c("selected_hunterID", "surveyID", "state", "county", "harvested_date"),
          values_from = retrieved,
          names_from = sp) %>% 
        mutate(over = "N")) %>% 
    relocate(over, .after = "harvested_date") %>% 
    group_by(selected_hunterID) %>% 
    mutate(n = n()) %>% 
    ungroup() %>% 
    filter(n >= 2) %>% 
    group_by(selected_hunterID) %>% 
    filter("Y" %in% over) %>% 
    ungroup() %>% 
    arrange(selected_hunterID) %>% 
    rename(
      hunterID = selected_hunterID,
      harvest_date = harvested_date) %>% 
    left_join(
      tibble(
        st = state.abb,
        state = state.name),
      by = "state") %>% 
    relocate(st, .before = "county") %>% 
    select(-c("state", "n")) %>% 
    arrange(hunterID, harvest_date) %>% 
    group_by(hunterID) %>% 
    mutate(
      color = 
        ifelse(
          cur_group_id() %% 2 == 0,
          "odd",
          "even"),
      ID = 
        row_number()) %>% 
    ungroup() %>% 
    relocate(ID, .before = "hunterID"), 
  extensions = "Buttons",
  options = 
    list(
      dom = "Bfrti",
      buttons = c("csv", "excel", "pdf"),
      ordering = F, 
      pageLength = -1,
      columnDefs = list(list(visible = F, targets = c(13))),
      scrollX = "1100px",
      scrollY = "500px"),
  width = "1100px",
  height = "500px") %>% 
  formatStyle(
    "color",
    target = "row",
    backgroundColor = styleEqual(c("odd", "even"), c("white", "lightgray"))) %>% 
  formatStyle(
    "over",
    backgroundColor = styleEqual("Y", "pink")) 

```

\  
\  
\  
\  
\  
\  
\  
\  
\  
\  
\  
\  
\  
\  
\
\
\
\
\


## Identify out-of-season take

What harvest dates in the daily data fell outside of the legal hunting season per species and state?

```{r, openclose2, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center", echo  = F}

openclose(get(names(tibblelist[2])), get(names(tibblelist[1])), summary = T) %>% 
  rename(
    sp = sp_group_estimated,
    state = sampled_state) %>% 
  left_join(
    tibble(
      state = state.name,
      state_abbr = state.abb),
    by = "state") %>% 
  mutate(prop = n/sum(n)) %>% 
  group_by(state) %>% 
  mutate(
    sum_n = sum(n),
    sum_prop = sum(prop)) %>% 
  ungroup() %>% 
  ggplot() + 
  geom_bar(
    aes(x = reorder(state_abbr, -sum_prop), y = prop, fill = error), 
    stat = "identity") + 
  geom_text(
    aes(x = reorder(state_abbr, -sum_prop), 
        y = sum_prop, 
        label = sum_n, 
        angle = 90),
    vjust = 0.2, hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(-0, 0.4))) +
  theme_classic() + 
  labs(
    y = "Proportion", 
    x = "State", 
    fill = "Error type") +
  theme(legend.position = "bottom") +
  scale_fill_manual(values = met.brewer("Hokusai3", 3))

```

```{r, openclose1, message = FALSE, warning = FALSE, echo = F}
datatable(openclose(get(names(tibblelist[2])), get(names(tibblelist[1])), summary = T))
```

## Error summary

Season data can include errors such as overbags (bag value over what is the legal limit), overdays (days hunted more than what is possible during the regular season), or both. Errors detected in daily data may include overbags, overdays, early hunts (hunting entry recorded before the season opens), and/or late hunts (hunting entry recorded after the season ended).

```{r, proofandcorrect, message = FALSE, warning = FALSE, echo = FALSE, include = FALSE}

# Read in the manually partyproofed daily data
party_proofed <-
  read_csv(paste0(params$partypath, "party_proofed_", params$year, ".csv"))

# Proof and correct the daily data
daily_proofed <- proofHS(party_proofed, get(names(tibblelist[1])))
rm(party_proofed)
daily_corrected <- correctHS(daily_proofed)

# Proof and correct the season data
season_proofed <- proofHS(get(names(tibblelist[3])), get(names(tibblelist[1])))
season_corrected <- correctHS(season_proofed)
```

### Season

```{r, errors_season, message = FALSE, warning = FALSE, echo = F, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center"}

errorsHS <-
  function(data){
    data %>% 
      select(errors) %>% 
      filter(errors != "none") %>% 
      mutate(errors = ifelse(str_detect(errors, "-"), "2+ errors", errors)) %>% 
      group_by(errors) %>% 
      summarize(n = n()) %>% 
      ungroup() %>% 
      mutate(prop = n/nrow(data %>% filter(errors != "none"))) %>% 
      ggplot() +
      geom_bar(aes(x = errors, y = prop), stat = "identity") + 
      geom_text(aes(x = errors, y = prop, label = n), nudge_y = .05) +
      labs(y = "Proportion", x = "Errors") +
      theme_classic()
  }

errorsHS(season_proofed)

```

### Daily

```{r, errors_daily, message = FALSE, warning = FALSE, echo = F, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center"}

errorsHS(daily_proofed)

```

# Retrieved 

## Retrieved map

The plots below show average retrieved values per state and species using the corrected Harvest Survey daily data.

```{r, retrievedmap, message = FALSE, warning = FALSE, echo = FALSE, dpi = 300, fig.asp = 1.1, fig.width = 8, fig.align = "center", echo  = F}

retrievedmap(daily_corrected)

```

## Birds retrieved

For the daily data, how many birds were retrieved on average per hunter? The figure and table below use the corrected data.

```{r, retrieved2, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center", echo  = F}

retrieved(daily_corrected, output = "plot", average = T) +
  theme(legend.position = "bottom") +
  scale_fill_manual(
    values = 
      met.brewer("Hokusai3", 
                 length(unique(daily_corrected$sp_group_estimated))))

datatable(retrieved(daily_corrected, average = T))
```

## Popular species

What is the proportion of birds that were successfully hunted? Each hunter's pursued species were grouped for this visualization. The corrected daily data are used.

```{r, bagspp1, message = FALSE, warning = FALSE, fig.width = 9, fig.height = 6, out.width = 700, dpi = 300, fig.align = "center", echo = F}

bagspp(daily_corrected, output = "success")
```


## Days hunted

In the daily data, how many days were spent hunting per species on average for each hunter? The corrected data are used.

```{r, huntdays3, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center", echo = F}

huntdays(daily_corrected, type = "species", output = "plot", average = T)
```

How about by state?

```{r, huntdays2, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center", echo = F}

huntdays(daily_corrected, output = "plot", average = T) +
  theme(legend.position = "bottom") + 
  scale_fill_manual(
    values = met.brewer("Hokusai3",
                        length(unique(daily_corrected$sp_group_estimated))))
```

```{r, huntdays1, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center", echo = F}

datatable(huntdays(daily_corrected, average = T))
```

## Comparing submitted vs. non-submit

What is the relationship between number of birds retrieved and number of days spent hunting when data are divided into 4 submission groups? The corrected daily and season data are used in the figures below. Daily retrieved values and days spent hunting were summed for direct comparison to season data.

```{r, compare1, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center", echo = F}
compare(daily_corrected, season_corrected, type = "line") +
  # Added for line clarity
  new_scale_color() +
  stat_smooth(
    aes(color = type), method = "lm", size = 1, alpha = 0.3) +
  scale_color_manual(
    name = "Type",
    labels = c("Daily non-submit", "Daily submit", "Season non-submit", 
               "Season submit"),
    values = c("orange", "green", "blue", "purple"))
```

What is the distribution of number of days hunted per submission group? Bubbles represent number of birds retrieved and red lines indicate mean values. Each bubble is a hunter's record per state and species.

```{r, compare2, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center", echo = F}
compare(daily_corrected, season_corrected, type = "days")
```

What is the distribution of number of birds retrieved per submission group? Bubbles represent number of days hunted and red lines indicate mean values. Each bubble is a hunter's record per state and species.

```{r, compare3, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center", echo = F}
compare(daily_corrected, season_corrected, type = "retrieved")
```
