---
title: "Online Harvest Survey Analytics Report"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc: true
    number_sections: true
params:
  inpath:
    value: x
  year:
    value: x
---

```{r, libs, message = FALSE, warning = FALSE, echo = FALSE}

library(tidyverse)
library(lubridate)
library(viridis)
library(MetBrewer)
library(treemapify)

# Input path
inpath <- params$inpath

# Read data 
invisible(read_dhs(inpath, year = as.character(params$year)))

# Add seaducks to the season metadata
all_seasons <- paste0("all_seasons_", as.character(params$year))
invisible(assign(all_seasons, add_seaducks(get(all_seasons)), envir = .GlobalEnv))

# Write tibble names to list for function compatibility
tibblelist <-
  vector("list", 3) %>% 
  set_names(
    all_seasons,
    paste0("daily_records_", as.character(params$year)),
    paste0("season_totals_", as.character(params$year)))
```

## Introduction

This is the `r params$year` survey analytics report for Harvest Survey online data.

## Response lag

What is the distribution of response lag?

```{r, responselag1, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center", echo = F}
responselag(get(names(tibblelist[2])), type = "count")
```

What is the relationship between time lag and number of birds retrieved?

```{r, responselag2, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center", echo = F}
responselag(get(names(tibblelist[2])), type = "lag")
```

What is the relationship between response date and harvest date? Larger and darker circles indicate more birds retrieved. The dotted lines are guides to show (from top to bottom), a time lag of 0, 30, 60, 90, and 120 days.

```{r, responselag3, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center", echo = F}
responselag(get(names(tibblelist[2])), type = "date")
```


## Retrieved birds by number of days hunted

In the daily data, what is the relationship between number of birds retrieved and number of days spent hunting?

```{r, bagdays2, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 4, dpi = 300, out.width = 500, fig.align = "center", echo = F}
bagdays(get(names(tibblelist[2])), output = "plot")
```

```{r, bagdays1, message = FALSE, warning = FALSE, echo = F}
DT::datatable(bagdays(get(names(tibblelist[2])), output = "table"))
```


## Harvest over time

### Daily

```{r, bagovertime_d, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 12, dpi = 300, out.width = 500, fig.align = "center", echo = F}

get(names(tibblelist[2])) %>% 
  mutate(
    sp_group_estimated =
      ifelse(
        str_detect(sp_group_estimated, "Sea"),
        "Sea Ducks",
        sp_group_estimated)) %>% 
  group_by(harvested_date, sp_group_estimated) %>% 
  summarize(sum_daily_retrieved = sum(retrieved)) %>% 
  ungroup() %>% 
  ggplot(
    aes(x = harvested_date, y = sum_daily_retrieved, 
        color = sp_group_estimated, fill = sp_group_estimated)) + 
  geom_jitter(alpha = 0.3) +
  geom_line() +
  labs(x = "Date harvested", y = "Number of birds retrieved") +
  theme_classic() +
  theme(legend.position = "none") +
  scale_fill_manual(
    values = 
      met.brewer(
        "Hokusai3",
        length(unique(get(names(tibblelist[2]))$sp_group_estimated)))) +
  scale_color_manual(
    values = 
      met.brewer(
        "Hokusai3",
        length(unique(get(names(tibblelist[2]))$sp_group_estimated)))) +
  facet_wrap(~sp_group_estimated, ncol = 1) 
  
```

### Weekly

```{r, bagovertime_w, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 12, dpi = 300, out.width = 500, fig.align = "center", echo = F}

get(names(tibblelist[2])) %>% 
  mutate(
    sp_group_estimated =
      ifelse(
        str_detect(sp_group_estimated, "Sea"),
        "Sea Ducks",
        sp_group_estimated)) %>% 
  mutate(harvested_wk = lubridate::week(harvested_date)) %>% 
  group_by(harvested_wk, sp_group_estimated) %>% 
  summarize(sum_weekly_retrieved = sum(retrieved)) %>% 
  ungroup() %>% 
  ggplot(
    aes(x = harvested_wk, y = sum_weekly_retrieved, 
        color = sp_group_estimated, fill = sp_group_estimated)) + 
  geom_jitter(alpha = 0.3) +
  geom_line() +
  labs(x = "Week harvested", y = "Number of birds retrieved") +
  theme_classic() +
  theme(legend.position = "none") +
  scale_fill_manual(
    values = 
      met.brewer(
        "Hokusai3",
        length(unique(get(names(tibblelist[2]))$sp_group_estimated)))) +
  scale_color_manual(
    values = 
      met.brewer(
        "Hokusai3",
        length(unique(get(names(tibblelist[2]))$sp_group_estimated)))) +
  facet_wrap(~sp_group_estimated, ncol = 1) 
  
```
